Minimizing post-shock forecasting error through aggregation of outside information

### 2021-02-04 Revision/manuscript.tex
everything looks good

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 7cm, width = 16.8cm]{FIG3.pdf}
    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and violet line represent real data and fitted line, respectively.}
    \label{Fig3}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

@@

We can extend the proposed methodology to forecast the response $m\geq 2$ time points ahead. In this setting, there are two cases. In the first case, we suppose that there is no additional shock after $T_1^*+1$. Then, the forecast boils down to standard $m$-ahead forecast in time series. In the second case, we assume that the time series under study will experience an additional additive shock at $T_1^* + m$, say $\alpha_1^{(m)}$. Users now construct the donor pool to consist of time series that experience shocks similar to  $\alpha_1^{(m)}$. Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(m)}$.  The adjusted forecast at $t = T_1^* + m$ is
$
  \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^2 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}
$
where the future covariates are themselves forecasted. The additional forecasting variability may  render such an adjustment approach useless.

>>>>

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[height = 7cm, width = 16.8cm]{FIG3.pdf}
    \caption{November 11th, 2020 post-shock forecasts for stock price of Apple Inc. Black dots and violet line represent real data and fitted line, respectively. We did not include forecast at $t=T_1^*+1$ for better visualization of post-shock forecast at $t=T_1^*+2$. The dotted line connects the unadjusted forecast at $t=T_1^*$ with the forecast at $t=T_1^*+2$. Our donor pool suggested that the shock effect take place at $t=T_1^*+2$ in this example.}
    \label{Fig3}
  \end{center}  
  \vspace{-.6cm}
\end{figure*}

@@

We can extend the proposed methodology to forecast the response $m\geq 2$ time points ahead. In this setting, there are two cases. In the first case, we suppose that there is no additional shock after $T_1^*+1$. Then, the forecast boils down to standard $m$-ahead forecast in time series. In the second case, we assume that the time series under study will experience an additional additive shock at $T_1^* + m$, say $\alpha_1^{(m)}$. Users now construct the donor pool to include time series that experienced shocks similar to  $\alpha_1^{(m)}$. Let the resulting estimator using one of  three weighting scheme be $\hat{\alpha}_1^{(m)}$.  The adjusted forecast at $t = T_1^* + m$ is
$
 \hat{y}^2_{1, T_1^*+m}=\hat{\eta}_1 + \hat{\phi}_1 \hat{y}_{1, T_1^* + m - 1}^1 + \hat{\theta}_1' \mathbf{x}_{1, T_1^* +m} + \hat{\alpha}_1^{(m)}
$
where the future covariates are themselves forecasted. The additional forecasting variability may  render such an adjustment approach useless.
